### 2018-06-04 README.Rmd
start of work on built check fixes, still need to add documentation for functions and tests

The goal of salinity is to ...

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```

>>>>

This package was used the generate the manuscript "Effect of drought-induced salinization on wetland methane emissions, gross
  ecosystem photosynthesis, and their interactions." by Samuel D. Chamberlain et. al. The /data folder contains half-hourly eddy covariance files used in the analysis, the /R folder contains scripts used to process data and information theory functions, and the /vignettes folder contains the Markdown and bibiography files used to generate the manuscript.

## Installation

You can install salinity from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("samdchamberlain/salinity")
```

## How to Run
Load package into RStudio and open the 'manuscript.Rmd' within the /vignettes folder. Using RStudio, click the 'Knit' button at the top of the console and this manuscript, and analyses herein, will be re-created.
